Verifying Demonstrations

### 2017-09-29 protocol.tex
Starts outlining the roles
Adds more roles in protocol
Adds intro, storage and temporal solution to protocol

\dots

\subsubsection{Temporal eligibility}

\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
  set}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
} of objects.
If some objects in the set relate to known points in time, then the partial 
order relates the data to the time of the event.
This allows us to \emph{verify the data temporally}.

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}.
(See \cref{PosetGraph}.)
For generality, we will use the terminology of 
\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
structure \iac{tposet}.

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
protest, then the relation will guarantee that \(p_A, p_B\) were created before 
the end of the protest.
Then we know that they cannot have been created after the event.

For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
in their proofs, e.g.\ \(t_s\) in \cref{PosetGraph}.
This means that if \(t_s\) is sufficiently close (time-wise) to the protest and 
has sufficiently high entropy, then Alice or Bob cannot create a proof and keep 
it for a future protest.

They can use an older value (pick one from the history of the \ac{tposet}) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval, i.e.\ possibly before the protest.

\subsubsection{Spatial eligibility}

@@

>>>>

We will start by giving an overview of the protocol.
We have a number of participants.
We have a cothority who provide the storage in a decentralized manner.
The cothority should consist of independent actors, preferably with conflicting 
interests so that they will not collude.
We have Alice the organizer and Bob the participant who are both protesters.
We have the trustworthy journalist Jane who is present but not participating in 
the protest.
The protesters will witness each others participation proofs, e.g.\ Alice will 
witness Bob's proof and Bob will witness Alice's proof.
The result of witnessing a proof is a proof share (essentially a witness 
signature).
Jane will also participate in witnessing the protesters' proofs.
The witnessing is done through local interaction.
As soon as Alice and Bob have departed from the protest they upload their proofs 
(i.e.\ all proof shares) to the cothority for indefinite storage.
Since each proof consists of one proof share for each witness, each witness 
could potentially upload the proof share themselves to the cothority.
This would have the same effect but with added redundancy, in case Alice or Bob 
cannot upload them themselves.

\subsection{Location proofs and spatial eligibility}

@@

\subsection{Storage and temporal eligibility}

We will use the storage to provide temporal eligibility.
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
  set}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
} of objects.
(See \cref{PosetGraph}.)
If some objects in the set relate to known points in time, then the partial 
order relates the data to the time of the event.
This allows us to \emph{verify the data temporally}.
One primitive that fulfils these requirements is a blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
properties.
However, we will use the blockchain in our discussion for simplicity.

There are exactly two properties that we need.
The first property we need is decentralized, immutable storage with a general 
form of time-stamping.
I.e.\ once we commit something to the blockchain it will remain there and we do 
not have to trust any central authority.
We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
block appears approximately every 10 minutes.

The second property we need is an unpredictable number whose time of publication 
can be verified.
For this property, we will use the head of the blockchain.
The hash value of the head of the blockchain at a given time will be difficult 
to predict ahead of time.
%(See \cref{SecurityAnalysis} for a security analysis.)
We want to use this to ensure that proofs are created after a certain point in 
time.

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply commit their 
proofs to the blockchain as soon as possible after they have participated in the 
protest.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.
For \cref{CreatedAfterStart} Alice and Bob must include the hash value of a 
block in the blockchain.
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).
